---
title: "Study 2 Primary Analyses"
author: "Muji Chughtai"
date: "`r Sys.Date()`"
output: pdf_document
---

# Load in Required Packages and Data
```{r}
library(tidyverse)
library(here)
library(svglite)
library(lme4)
library(lmerTest)
library(emmeans)
library(reghelper)
library(lsr)
library(apaTables)

study2 <- read.csv(
  here("Data", "Analysis-Ready Data", "Study2_AnalysisData.csv")
)
Experience <- study2 %>%
  filter(Type == "Experience")
Expression <- study2 %>%
  filter(Type == "Expression")
```

# H1a - Perceieved Experience will Differ by Emotion
```{r}
model1a <- glm(Frequency ~ Emotion, data = Experience)
summary(model1a)
```

```{r}
model1a.emm <- emmeans(model1a, ~ Emotion)
pairs(model1a.emm)
confint(pairs(model1a.emm))
eff_size(model1a.emm, sigma = sigma(model1a), edf = df.residual(model1a))
```

# H1b - Perceieved Expression will Differ by Emotion
```{r}
model1b <- glm(Frequency ~ Emotion, data = Expression)
summary(model1b)
```

```{r}
model1b.emm <- emmeans(model1b, ~ Emotion)
pairs(model1b.emm)
confint(pairs(model1b.emm))
eff_size(model1b.emm, sigma = sigma(model1b), edf = df.residual(model1b))
```

# H2 - Connection when Perceving will Differ by Emotion
```{r}
model2 <- glm(Connection ~ Emotion, data = Expression)
summary(model2)
```

```{r}
model2.emm <- emmeans(model2, ~ Emotion)
pairs(model2.emm)
confint(pairs(model2.emm))
eff_size(model2.emm, sigma = sigma(model2), edf = df.residual(model2))
```

# H3 - Guilt will be Connecting in Communal but Disconnecting in Transactional
```{r}
Expression %>%
  filter(Emotion == "Guilt") %>%
  group_by(Relationship_Type) %>%
  summarize(
    t_test = list(t.test(Connection, mu = 0)),
    df = t_test[[1]]$parameter,
    estimate = t_test[[1]]$estimate,
    statistic = t_test[[1]]$statistic,
    p_value = t_test[[1]]$p.value,
    conf_int_low = t_test[[1]]$conf.int[1],
    conf_int_high = t_test[[1]]$conf.int[2],
    effect_size = as.numeric(cohensD(Connection, mu = 0))
  ) %>%
  ungroup()
```

# H4 - The differences in feelings of connection associated with expressing versus perceiving emotions will be larger for disengaging (versus engaging) emotions
```{r}
study1_comp <- read.csv(
  here("Data", "Analysis-Ready Data", "Study1_ComparisonData.csv")
)
study2_comp <- read.csv(
  here("Data", "Analysis-Ready Data", "Study2_ComparisonData.csv")
)

study1_comp <- study1_comp %>%
  filter(Type == "Expression")

study2_comp <- study2_comp %>%
  filter(Type == "Expression")

comp_data <- rbind(study1_comp, study2_comp)
```

```{r}
model4 <- glm(Connection ~ PE*Orientation, data = comp_data)
summary(model4)
confint(model4)
```

```{r}
model4.emm <- emmeans(model4, ~ PE*Orientation)
pairs(model4.emm)
confint(pairs(model4.emm))
eff_size(model4.emm, sigma = sigma(model4), edf = df.residual(model4))
```

# H5 - Connection will be Positively Associated with Perception, Especially for Communal Relationships
```{r}
model5a <- glm(Frequency ~ Connection, data = Expression)
summary(model5a)
confint(model5a)
```

```{r}
model5b <- glm(Frequency ~ Relationship_Type*Connection, data = Expression)
summary(model5b)
confint(model5b)
simple_slopes(model5b)

# Define the estimates and standard errors for the two simple slopes (Communal and Transactional)
communal_slope <- 0.4225
communal_se <- 0.0143

transactional_slope <- 0.3416
transactional_se <- 0.0165

# Degrees of freedom (df) based on model output (5064)
df <- 5064

# Calculate the critical t-value for 95% CI
alpha <- 0.05
t_value <- qt(1 - alpha / 2, df)

# Manually calculate the confidence intervals
communal_ci_lower <- communal_slope - t_value * communal_se
communal_ci_upper <- communal_slope + t_value * communal_se

transactional_ci_lower <- transactional_slope - t_value * transactional_se
transactional_ci_upper <- transactional_slope + t_value * transactional_se

# Display results
cat("Communal Slope CI: [", communal_ci_lower, ",", communal_ci_upper, "]\n")
cat("Transactional Slope CI: [", transactional_ci_lower, ",", transactional_ci_upper, "]\n")
```

# Individual Emotions

## Experience
```{r}
model6 <- glm(Frequency ~ Emotion, data = Experience)
summary(model6)
```

```{r}
model6.emm <- emmeans(model6, ~ Emotion)
pairs(model6.emm)
confint(pairs(model6.emm))
eff_size(model6.emm, sigma = sigma(model6), edf = df.residual(model6))
```

## Expression
```{r}
model7 <- glm(Frequency ~ Emotion, data = Expression)
summary(model7)
```

```{r}
model7.emm <- emmeans(model7, ~ Emotion)
pairs(model7.emm)
confint(pairs(model7.emm))
eff_size(model7.emm, sigma = sigma(model7), edf = df.residual(model7))
```

## Connection
```{r}
model8 <- glm(Connection ~ Emotion, data = Expression)
summary(model8)
```

```{r}
model8.emm <- emmeans(model8, ~ Emotion)
pairs(model8.emm)
confint(pairs(model8.emm))
eff_size(model8.emm, sigma = sigma(model8), edf = df.residual(model8))
```

# Individual Emotions and Relationship Types

## Experience
```{r}
x <- Experience %>%
  ggplot(aes(x = factor(Relationship_Type, levels = c("Communal", "Transactional")),
             fill = factor(Emotion, levels = c("Respect", "Guilt", "Pride", "Anger")),
             y = Frequency)) +
    scale_fill_manual(values = c("Respect" = "#00356B", "Guilt" = "#A11FA2", 
                               "Pride" = "#F2A007", "Anger" = "#D32F2F")) +
  stat_summary(fun = "mean", geom = "col", color = "black", position = "dodge") +
  stat_summary(fun.data = "mean_cl_normal", geom = "errorbar",
               position = position_dodge(0.9), width = 0.25) +
  labs(title = "",
       x = "Relationship Type",
       y = "Frequency",
       fill = "Emotion") +
    coord_cartesian(ylim = c(0, 3.5)) + 
    theme_minimal() + 
    theme(
        legend.position = "bottom", 
        strip.text = element_text(size=14),
        axis.text = element_text(size=14),
        axis.title.y = element_text(size=14, vjust=0.35),
        axis.title.x = element_text(size=16),
        legend.title = element_text(size=16),
        legend.text = element_text(size=14),
        text = element_text(family = "Helvetica")
    )

ggsave(
  here("Figures", "Study 2", "Study2_Experience.svg"),
  x,
  width = 8,
  height = 6
)
```

```{r}
model9 <- glm(Frequency ~ Relationship_Type*Emotion, data = Experience)
summary(model9)
```

```{r}
model9.emm <- emmeans(model9, ~ Relationship_Type*Emotion)
pairs(model9.emm)
confint(pairs(model9.emm))
eff_size(model9.emm, sigma = sigma(model9), edf = df.residual(model9))
```

## Expression
```{r}
x <- Expression %>%
  ggplot(aes(x = factor(Relationship_Type, levels = c("Communal", "Transactional")),
             fill = factor(Emotion, levels = c("Respect", "Guilt", "Pride", "Anger")),
             y = Frequency)) +
    scale_fill_manual(values = c("Respect" = "#00356B", "Guilt" = "#A11FA2", 
                               "Pride" = "#F2A007", "Anger" = "#D32F2F")) +
  stat_summary(fun = "mean", geom = "col", color = "black", position = "dodge") +
  stat_summary(fun.data = "mean_cl_normal", geom = "errorbar",
               position = position_dodge(0.9), width = 0.25) +
  labs(title = "",
       x = "Relationship Type",
       y = "Frequency",
       fill = "Emotion") +
    coord_cartesian(ylim = c(0, 3.5)) + 
    theme_minimal() + 
    theme(
        legend.position = "bottom", 
        strip.text = element_text(size=14),
        axis.text = element_text(size=14),
        axis.title.y = element_text(size=14, vjust=0.35),
        axis.title.x = element_text(size=16),
        legend.title = element_text(size=16),
        legend.text = element_text(size=14),
        text = element_text(family = "Helvetica")
    )

ggsave(
  here("Figures", "Study 2", "Study2_Expression.svg"),
  x,
  width = 8,
  height = 6
)
```

```{r}
model10 <- glm(Frequency ~ Relationship_Type*Emotion, data = Expression)
summary(model10)
```

```{r}
model10.emm <- emmeans(model10, ~ Relationship_Type*Emotion)
pairs(model10.emm)
confint(pairs(model10.emm))
eff_size(model10.emm, sigma = sigma(model10), edf = df.residual(model10))
```

## Connection
```{r}
x <- Expression %>%
  ggplot(aes(x = factor(Relationship_Type, levels = c("Communal", "Transactional")),
             fill = factor(Emotion, levels = c("Respect", "Guilt", "Pride", "Anger")),
             y = Connection)) +
    scale_fill_manual(values = c("Respect" = "#00356B", "Guilt" = "#A11FA2", 
                               "Pride" = "#F2A007", "Anger" = "#D32F2F")) +
  stat_summary(fun = "mean", geom = "col", color = "black", position = "dodge") +
  stat_summary(fun.data = "mean_cl_normal", geom = "errorbar",
               position = position_dodge(0.9), width = 0.25) +
  labs(title = "",
       x = "Relationship Type",
       y = "Frequency",
       fill = "Emotion") +
    coord_cartesian(ylim = c(-2, 2)) + 
    theme_minimal() + 
    theme(
        legend.position = "bottom", 
        strip.text = element_text(size=14),
        axis.text = element_text(size=14),
        axis.title.y = element_text(size=14, vjust=0.35),
        axis.title.x = element_text(size=16),
        legend.title = element_text(size=16),
        legend.text = element_text(size=14),
        text = element_text(family = "Helvetica")
    )

ggsave(
  here("Figures", "Study 2", "Study2_Connection.svg"),
  x,
  width = 8,
  height = 6
)
```

```{r}
model11 <- glm(Connection ~ Relationship_Type*Emotion, data = Expression)
summary(model11)
```

```{r}
model11.emm <- emmeans(model11, ~ Relationship_Type*Emotion)
pairs(model11.emm)
confint(pairs(model11.emm))
eff_size(model11.emm, sigma = sigma(model11), edf = df.residual(model11))
```

# Full Descriptive Statistics
```{r}
# Experience
Experience.desc <- apa.2way.table(
  iv1 = Relationship_Type,
  iv2 = Emotion, 
  dv = Frequency,
  data = Experience
)

# Expression
Expression.desc <- apa.2way.table(
  iv1 = Relationship_Type,
  iv2 = Emotion, 
  dv = Frequency,
  data = Expression
)

# Connection
Connection.desc <- apa.2way.table(
  iv1 = Relationship_Type,
  iv2 = Emotion, 
  dv = Connection,
  data = Expression
)

Experience.desc
Expression.desc
Connection.desc
```