---
title: "Study 2 Primary Analyses"
author: "Muji Chughtai"
date: "`r Sys.Date()`"
output: pdf_document
---

# Load in Required Packages and Data
```{r}
library(tidyverse)
library(here)
library(svglite)
library(lme4)
library(lmerTest)
library(emmeans)
library(lsr)

study2 <- read.csv(
  here("Data", "Analysis-Ready Data", "Study2_AnalysisData.csv")
)
Experience <- study2 %>%
  filter(Type == "Experience")
Expression <- study2 %>%
  filter(Type == "Expression")
```

# Demographics

## Race/Ethnicity
```{r}
individuals <- study2 %>%
  distinct(PID, .keep_all = TRUE)

individuals %>%
  mutate(Race = if_else(grepl(",", Race), "10", Race)) %>%
  group_by(Race) %>%
  summarise(
    N = n(),
    Proportion = N / nrow(individuals)
  ) %>%
  arrange(desc(N))
```

## Age
```{r}
individuals %>%
  filter(!is.na(Age_4_TEXT)) %>%
  summarise(Min = min(Age_4_TEXT),
            Q1 = quantile(Age_4_TEXT, 0.25),
            Mean = mean(Age_4_TEXT),
            Median = median(Age_4_TEXT),
            Q3 = quantile(Age_4_TEXT, 0.75),
            Max = max(Age_4_TEXT),
            IQR = IQR(Age_4_TEXT),
            SD = sd(Age_4_TEXT),
            N = n())
```

## Gender
```{r}
individuals %>%
  group_by(Gender) %>%
  summarise(
    N = n(),
    Proportion = N / nrow(individuals)) %>%
  arrange(desc(N))
```

# Perceieved Experience

## Distributions and Summary Statistics
```{r}
Experience %>%
  filter(!is.na(Frequency)) %>%
  summarise(Min = min(Frequency),
            Q1 = quantile(Frequency, 0.25),
            Mean = mean(Frequency),
            Median = median(Frequency),
            Q3 = quantile(Frequency, 0.75),
            Max = max(Frequency),
            IQR = IQR(Frequency),
            SD = sd(Frequency),
            N = n())
```

```{r}
Experience %>%
  ggplot(aes(x = Frequency)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), bins = 5, fill = "#228B22", color = "black", ) +
  labs(title = "Frequency of Perceived Experience", x = "Frequency",
       y = "Percentage") + theme_minimal()
```

## Checking Normality of Residuals for the Full Model
```{r}
full.model <- glm(Frequency ~ Relationship_Type*Emotion, data = Experience)

x <- ggplot() +
  stat_qq(aes(sample = residuals(full.model)), distribution = qnorm) +
  stat_qq_line(aes(sample = residuals(full.model)), distribution = qnorm) +
  ggtitle("Q-Q Plot") +
  labs(title = "Residuals for Frequency of Perceived Experience",
       x = "Theoretical Quantiles",
       y = "Sample Quantiles") + theme_minimal()

ggsave(
  here("Figures", "Study 2", "Study2_Residuals_Experience.svg"),
  x,
  width = 8,
  height = 6
)
```

# Perceived Expression

## Distributions and Summary Statistics
```{r}
Expression %>%
  filter(!is.na(Frequency)) %>%
  summarise(Min = min(Frequency),
            Q1 = quantile(Frequency, 0.25),
            Mean = mean(Frequency),
            Median = median(Frequency),
            Q3 = quantile(Frequency, 0.75),
            Max = max(Frequency),
            IQR = IQR(Frequency),
            SD = sd(Frequency),
            N = n())
```

```{r}
Expression %>%
  ggplot(aes(x = Frequency)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), bins = 5, fill = "#228B22", color = "black", ) +
  labs(title = "Frequency of Perceived Expression", x = "Frequency",
       y = "Percentage") + theme_minimal()
```

## Checking Normality of Residuals for the Full Model
```{r}
full.model <- glm(Frequency ~ Relationship_Type*Emotion, data = Expression)

x <- ggplot() +
  stat_qq(aes(sample = residuals(full.model)), distribution = qnorm) +
  stat_qq_line(aes(sample = residuals(full.model)), distribution = qnorm) +
  ggtitle("Q-Q Plot") +
  labs(title = "Residuals for Frequency of Perceived Expression",
       x = "Theoretical Quantiles",
       y = "Sample Quantiles") + theme_minimal()

ggsave(
  here("Figures", "Study 2", "Study2_Residuals_Expression.svg"),
  x,
  width = 8,
  height = 6
)
```

# Connection

## Distributions and Summary Statistics
```{r}
Expression %>%
  filter(!is.na(Connection)) %>%
  summarise(Min = min(Connection),
            Q1 = quantile(Connection, 0.25),
            Mean = mean(Connection),
            Q3 = quantile(Connection, 0.75),
            Max = max(Connection),
            IQR = IQR(Connection),
            SD = sd(Connection),
            N = n())
```

## Checking Normality of Residuals for the Full Model
```{r}
full.model <- glm(Connection ~ Relationship_Type*Emotion, data = Expression)

ggplot() +
  stat_qq(aes(sample = residuals(full.model)), distribution = qnorm) +
  stat_qq_line(aes(sample = residuals(full.model)), distribution = qnorm) +
  ggtitle("Q-Q Plot") +
  labs(title = "Residuals for Feelings of Connection when Perceiving",
       x = "Theoretical Quantiles",
       y = "Sample Quantiles") + theme_minimal()

ggsave(
  here("Figures", "Study 2", "Study2_Residuals_Connection.svg"),
  x,
  width = 8,
  height = 6
)

```

# Checking Random Effects of Participant

## Experience
```{r}
model <- lmer(Frequency ~ 1 + (1|PID), data = Experience)
summary(model)

ICC <- 0.04001 / (0.04001 + 1.30988);ICC
```

## Expression
```{r}
model <- lmer(Frequency ~ 1 + (1|PID), data = Expression)
summary(model)

ICC <- 0.03281 / (0.03281 + 1.34244);ICC
```

## Connection
```{r}
model <- lmer(Connection ~ 1 + (1|PID), data = Expression)
summary(model)

ICC <- 0.09276 / (0.09276 + 1.23911);ICC
```

# Testing Preregistered Primary Hypotheses

## H1 - Emotion Expression will be Perceived More in Communal vs. Transactional Relationships
```{r}
model1 <- glm(Frequency ~ Relationship_Type, data = Expression)
summary(model1)
confint(model1)
cohensD(Frequency ~ Relationship_Type, data = Expression)
```

## H2 - Emotion Experience will be Perceived More in Communal vs. Transactional Relationships
```{r}
model2 <- glm(Frequency ~ Relationship_Type, data = Experience)
summary(model2)
confint(model2)
cohensD(Frequency ~ Relationship_Type, data = Experience)
```

## H3 - Experience will be Higher than Expression, Especially for Transactional Relationships and Disengaging Emotions
```{r}
model3a <- glm(Frequency ~ Type, data = study2)
summary(model3a)
confint(model3a)
cohensD(Frequency ~ Type, data = study2)
```

```{r}
model3b <- glm(Frequency ~ Type*Relationship_Type, data = study2)
summary(model3b)
confint(model3b)
```

```{r}
model3b.emm <- emmeans(model3b, ~ Type*Relationship_Type)
pairs(model3b.emm)
confint(pairs(model3b.emm))
eff_size(model3b.emm, sigma = sigma(model3b), edf = df.residual(model3b))
```

```{r}
model3c <- glm(Frequency ~ Type*Orientation, data = study2)
summary(model3c)
confint(model3c)
```

```{r}
model3c.emm <- emmeans(model3c, ~ Type*Orientation)
pairs(model3c.emm)
confint(pairs(model3c.emm))
eff_size(model3c.emm, sigma = sigma(model3c), edf = df.residual(model3c))
```

## H4 - Connection will be Higher in Communal vs. Transactional Relationships
```{r}
model4 <- glm(Connection ~ Relationship_Type, data = Expression)
summary(model4)
confint(model4)
cohensD(Connection ~ Relationship_Type, data = Expression)
```

## H5 - Connection will be Higher for Engaging vs Disengaging Emotions
```{r}
model5 <- glm(Connection ~ Orientation, data = Expression)
summary(model5)
confint(model5)
cohensD(Connection ~ Orientation, data = Expression)
```

## H6 - Participants will Feel more Connected when Expressing Versus Perceiving
```{r}
study1_comp <- read.csv(
  here("Data", "Analysis-Ready Data", "Study1_ComparisonData.csv")
)
study2_comp <- read.csv(
  here("Data", "Analysis-Ready Data", "Study2_ComparisonData.csv")
)

study1_comp <- study1_comp %>%
  filter(Type == "Expression")

study2_comp <- study2_comp %>%
  filter(Type == "Expression")

comp_data <- rbind(study1_comp, study2_comp)
```

```{r}
model6 <- glm(Connection ~ PE, data = comp_data)
summary(model6)
confint(model6)
cohensD(Connection ~ PE, data = comp_data)
```