---
title: "Study 1 Primary Analyses"
author: "Muji Chughtai"
date: "`r Sys.Date()`"
output: pdf_document
---

# Load in Required Packages and Data
```{r}
library(tidyverse)
library(here)
library(svglite)
library(lme4)
library(lmerTest)
library(emmeans)
library(reghelper)
library(lsr)

study1 <- read.csv(
  here("Data", "Analysis-Ready Data", "Study1_AnalysisData.csv")
)
Experience <- study1 %>%
  filter(Type == "Experience")
Expression <- study1 %>%
  filter(Type == "Expression")
```

# Demographics

## Race/Ethnicity
```{r}
individuals <- study1 %>%
  distinct(PID, .keep_all = TRUE)

individuals %>%
  group_by(Ethnicity.simplified) %>%
  summarise(
    N = n(),
    Proportion = N / nrow(individuals)) %>%
    arrange(desc(N))
```

## Age
```{r}
individuals %>%
  filter(!is.na(Age)) %>%
  summarise(Min = min(Age),
            Q1 = quantile(Age, 0.25),
            Mean = mean(Age),
            Median = median(Age),
            Q3 = quantile(Age, 0.75),
            Max = max(Age),
            IQR = IQR(Age),
            SD = sd(Age),
            N = n())
```

## Sex
```{r}
individuals %>%
  group_by(Sex) %>%
  summarise(
    N = n(),
    Proportion = N / nrow(individuals)) %>%
  arrange(desc(N))
```

# Experience

## Distributions and Summary Statistics
```{r}
Experience %>%
  filter(!is.na(Frequency)) %>%
  summarise(Min = min(Frequency),
            Q1 = quantile(Frequency, 0.25),
            Mean = mean(Frequency),
            Median = median(Frequency),
            Q3 = quantile(Frequency, 0.75),
            Max = max(Frequency),
            IQR = IQR(Frequency),
            SD = sd(Frequency),
            N = n())
```

```{r}
Experience %>%
  ggplot(aes(x = Frequency)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), bins = 5, fill = "#228B22", color = "black", ) +
  labs(title = "Frequency of Experience", x = "Frequency",
       y = "Percentage") + theme_minimal()
```

## Checking Normality of Residuals for the Full Model
```{r}
full.model <- glm(Frequency ~ Relationship_Type*Emotion, data = Experience)

x <- ggplot() +
  stat_qq(aes(sample = residuals(full.model)), distribution = qnorm) +
  stat_qq_line(aes(sample = residuals(full.model)), distribution = qnorm) +
  ggtitle("Q-Q Plot") +
  labs(title = "Residuals for Frequency of Experience",
       x = "Theoretical Quantiles",
       y = "Sample Quantiles") + theme_minimal()


ggsave(
  here("Figures", "Study 1", "Study1_Residuals_Experience.svg"),
  x,
  width = 8,
  height = 6
)
```

# Expression

## Distributions and Summary Statistics
```{r}
Expression %>%
  filter(!is.na(Frequency)) %>%
  summarise(Min = min(Frequency),
            Q1 = quantile(Frequency, 0.25),
            Mean = mean(Frequency),
            Median = median(Frequency),
            Q3 = quantile(Frequency, 0.75),
            Max = max(Frequency),
            IQR = IQR(Frequency),
            SD = sd(Frequency),
            N = n())
```

```{r}
Expression %>%
  ggplot(aes(x = Frequency)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), bins = 5, fill = "#228B22", color = "black", ) +
  labs(title = "Frequency of Expression", x = "Frequency",
       y = "Percentage") + theme_minimal()
```

## Checking Normality of Residuals for the Full Model
```{r}
full.model <- glm(Frequency ~ Relationship_Type*Emotion,
                  data = Expression)

x <- ggplot() +
  stat_qq(aes(sample = residuals(full.model)), distribution = qnorm) +
  stat_qq_line(aes(sample = residuals(full.model)), distribution = qnorm) +
  ggtitle("Q-Q Plot") +
  labs(title = "Residuals for Frequency of Expression",
       x = "Theoretical Quantiles",
       y = "Sample Quantiles") + theme_minimal()

ggsave(
  here("Figures", "Study 1", "Study1_Residuals_Expression.svg"),
  x,
  width = 8,
  height = 6
)
```

# Connection

## Distributions and Summary Statistics
```{r}
Expression %>%
  filter(!is.na(Connection)) %>%
  summarise(Min = min(Connection),
            Q1 = quantile(Connection, 0.25),
            Mean = mean(Connection),
            Q3 = quantile(Connection, 0.75),
            Max = max(Connection),
            IQR = IQR(Connection),
            SD = sd(Connection),
            N = n())
```

## Checking Normality of Residuals for the Full Model
```{r}
full.model <- glm(Connection ~ Relationship_Type*Emotion, data = Expression)

x <- ggplot() +
  stat_qq(aes(sample = residuals(full.model)), distribution = qnorm) +
  stat_qq_line(aes(sample = residuals(full.model)), distribution = qnorm) +
  ggtitle("Q-Q Plot") +
  labs(title = "Residuals for Feelings of Connection when Expressing",
       x = "Theoretical Quantiles",
       y = "Sample Quantiles") + theme_minimal()

ggsave(
  here("Figures", "Study 1", "Study1_Residuals_Connection.svg"),
  x,
  width = 8,
  height = 6
)
```

```{r}
Expression %>%
  ggplot(aes(x = Connection)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), bins = 5, fill = "#228B22", color = "black", ) +
  labs(title = "Feelings of Connection when Expressing", x = "Frequency",
       y = "Percentage") + theme_minimal()
```

# Checking Random Effects of Participant
## Experience
```{r}
model <- lmer(Frequency ~ 1 + (1|PID), data = Experience)
summary(model)

ICC <- 0.04052 / (0.04052 + 1.37639);ICC
```

## Expression
```{r}
model <- lmer(Frequency ~ 1 + (1|PID), data = Expression)
summary(model)

ICC <- 0.0864 / (0.0864 + 1.3500);ICC
```

## Connection
```{r}
model <- lmer(Connection ~ 1 + (1|PID), data = Expression)
summary(model)

ICC <- 0.09599 / (0.09599 + 1.15015);ICC
```

# Testing Preregistered Primary Hypotheses

## H1 - Engaging Emotions will be Experienced More in Communal vs. Transactional Relationships

## H2 - In Communal Relationships, Engaging Emotions will be Experienced More than Disengaging Ones
```{r}
model1 <- glm(Frequency ~ Relationship_Type*Orientation,
              data = Experience)
summary(model1)
confint(model1)
```

```{r}
model1.emm <- emmeans(model1, ~ Relationship_Type*Orientation)
pairs(model1.emm)
confint(pairs(model1.emm))
eff_size(model1.emm, sigma = sigma(model1), edf = df.residual(model1))
```

## H3 - Engaging Emotions will be Expressed More in Communal vs. Transactional Relationships

## H4 - In Communal Relationships, Engaging Emotions will be Expressed More than Disengaging Ones
```{r}
model2 <- glm(Frequency ~ Relationship_Type*Orientation,
              data = Expression)
summary(model2)
confint(model2)
```

```{r}
model2.emm <- emmeans(model2, ~ Relationship_Type*Orientation)
pairs(model2.emm)
confint(pairs(model2.emm))
eff_size(model2.emm, sigma = sigma(model2), edf = df.residual(model2))
```

## H5 - Feelings of Connection will be Higher in Communal vs. Transactional Relationships
```{r}
model5 <- glm(Connection ~ Relationship_Type, data = Expression)
summary(model5)
confint(model5)
cohensD(Connection ~ Relationship_Type, data = Expression)
```

## H6 - Feelings of Connection will be Higher for Engaging vs. Disengaging Emotions
```{r}
model6 <- glm(Connection ~ Orientation, data = Expression)
summary(model6)
confint(model6)
cohensD(Connection ~ Orientation, data = Expression)
```

## H7 - Feelings of Connection will be Positively Related to Frequency of Expression in Communal (but not Transactional) Relationships
```{r}
model4 <- glm(Frequency ~ Relationship_Type*Connection,
              data = Expression)
summary(model4)
confint(model4)
simple_slopes(model4)

# Define the estimates and standard errors for the two simple slopes (Communal and Transactional)
communal_slope <- 0.5230
communal_se <- 0.0144

transactional_slope <- 0.3794
transactional_se <- 0.0187

# Degrees of freedom (df) based on model output (4553)
df <- 4553

# Calculate the critical t-value for 95% CI
alpha <- 0.05
t_value <- qt(1 - alpha / 2, df)

# Manually calculate the confidence intervals
communal_ci_lower <- communal_slope - t_value * communal_se
communal_ci_upper <- communal_slope + t_value * communal_se

transactional_ci_lower <- transactional_slope - t_value * transactional_se
transactional_ci_upper <- transactional_slope + t_value * transactional_se

# Display results
cat("Communal Slope CI: [", communal_ci_lower, ",", communal_ci_upper, "]\n")
cat("Transactional Slope CI: [", transactional_ci_lower, ",", transactional_ci_upper, "]\n")
```