---
title: "Study 4 Exploratory Analyses"
author: "Muji Chughtai"
date: '`r Sys.Date()`'
output: pdf_document
---

# Load in Required Packages and Data
```{r}
library(tidyverse)
library(here)
library(svglite)
library(lme4)
library(lmerTest)
library(emmeans)
library(lsr)

study4 <- read.csv(
  here("Data", "Analysis-Ready Data", "Study4_AnalysisData.csv")
)
Experience <- study4 %>%
  filter(Exp_Type == "Experience")
Expression <- study4 %>%
  filter(Exp_Type == "Expression")
```

# Willingness

## Distributions and Summary Statistics
```{r}
Expression %>%
  filter(Hyp_Recall == "Recall") %>%
  filter(!is.na(Willing)) %>%
  summarise(Min = min(Willing),
            Q1 = quantile(Willing, 0.25),
            Mean = mean(Willing),
            Median = median(Willing),
            Q3 = quantile(Willing, 0.75),
            Max = max(Willing),
            IQR = IQR(Willing),
            SD = sd(Willing),
            N = n())
```

```{r}
Expression %>%
  filter(Hyp_Recall == "Recall") %>%
  ggplot(aes(x = Willing)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), bins = 5, fill = "#228B22", color = "black", ) +
  labs(title = "Willingness to Express", x = "Frequency",
       y = "Percentage") + theme_minimal()
```

## Checking Normality of Residuals for the Full Model
```{r}
full.model <- glm(Frequency ~ Relationship_Type*Emotion, data = subset(Expression, Hyp_Recall == "Recall"))

x <- ggplot() +
  stat_qq(aes(sample = residuals(full.model)), distribution = qnorm) +
  stat_qq_line(aes(sample = residuals(full.model)), distribution = qnorm) +
  ggtitle("Q-Q Plot") +
  labs(title = "Residuals for Willingness of Partners to Express",
       x = "Theoretical Quantiles",
       y = "Sample Quantiles") + theme_minimal()

ggsave(
  here("Figures", "Study 4", "Study4_Residuals_Willing.svg"),
  x,
  width = 8,
  height = 6
)
```

# Checking Random Effects of Participants
```{r}
model <- lmer(Willing ~ 1 + (1|PID), data = subset(Expression, Hyp_Recall == "Recall"))
summary(model)

ICC <- 0.1409 / (0.1409 + 1.1591);ICC
```

# Testing Preregistered Exploratory Hypotheses

## H1 - Willingness to Express will be Higher in Communal Relationships
```{r}
model1 <- glm(Willing ~ Relationship_Type, data = subset(Expression, Hyp_Recall == "Recall"))
summary(model1)
confint(model1)
cohensD(Affirming ~ Relationship_Type, data = subset(Expression, Hyp_Recall == "Recall"))
```

```{r}
x <- Expression %>%
  filter(!is.na(Willing)) %>%
  filter(Hyp_Recall == "Recall") %>%
  ggplot(aes(x = factor(Relationship_Type, levels = c("Communal", "Transactional")),
             fill = factor(Emotion, levels = c("Love", "Joy", "Sadness", "Hurt")),
             y = Willing)) +
    scale_fill_manual(values = c("Love" = "#E57373", "Joy" = "#FFCA28",  
                               "Sadness" = "#64B5F6", "Hurt" = "#AF7AC5")) +
  stat_summary(fun = "mean", geom = "col", color = "black", position = "dodge") +
  stat_summary(fun.data = "mean_cl_normal", geom = "errorbar",
               position = position_dodge(0.9), width = 0.25) +
  labs(title = "",
       x = "Relationship Type",
       y = "Rating",
       fill = "Emotion") +
    coord_cartesian(ylim = c(-2, 2)) + 
    theme_minimal() + 
    theme(
        legend.position = "bottom", 
        strip.text = element_text(size=14),
        axis.text = element_text(size=14),
        axis.title.y = element_text(size=14, vjust=0.35),
        axis.title.x = element_text(size=16),
        legend.title = element_text(size=16),
        legend.text = element_text(size=14),
        text = element_text(family = "Helvetica")
    )

ggsave(
  here("Figures", "Study 4", "Study4_Willing.svg"),
  x,
  width = 8,
  height = 6
)
```

## H2 - Hypothetical Connection will be Less than Recalled Connection
```{r}
model2 <- glm(Connection ~ Hyp_Recall, data = Expression)
summary(model2)
confint(model2)
cohensD(Connection ~ Hyp_Recall, data = Expression)
```

```{r}
Expression %>%
  group_by(Hyp_Recall) %>%
  summarize(
    t_test = list(t.test(Connection, mu = 0)),
    estimate = t_test[[1]]$estimate,
    statistic = t_test[[1]]$statistic,
    p_value = t_test[[1]]$p.value,
    conf_int_low = t_test[[1]]$conf.int[1],
    conf_int_high = t_test[[1]]$conf.int[2],
    df = t_test[[1]]$parameter,
    effect_size = as.numeric(cohensD(Connection, mu = 0))
  ) %>%
  ungroup()
```

## H3 - Hypothetical Drawing Close will be Less than Recalled Connection
```{r}
model3 <- glm(DrawClose ~ Hyp_Recall, data = Expression)
summary(model3)
confint(model3)
cohensD(DrawClose ~ Hyp_Recall, data = Expression)
```

```{r}
Expression %>%
  group_by(Hyp_Recall) %>%
  summarize(
    t_test = list(t.test(DrawClose, mu = 0)),
    estimate = t_test[[1]]$estimate,
    statistic = t_test[[1]]$statistic,
    p_value = t_test[[1]]$p.value,
    conf_int_low = t_test[[1]]$conf.int[1],
    conf_int_high = t_test[[1]]$conf.int[2],
    df = t_test[[1]]$parameter,
    effect_size = as.numeric(cohensD(DrawClose, mu = 0))
  ) %>%
  ungroup()
```

## H4 - HypotheticalAffirming will be Less than Recalled Affirming
```{r}
model4 <- glm(Affirming ~ Hyp_Recall, data = Expression)
summary(model4)
confint(model4)
cohensD(Affirming ~ Hyp_Recall, data = Expression)
```

```{r}
Expression %>%
  group_by(Hyp_Recall) %>%
  summarize(
    t_test = list(t.test(Affirming, mu = 0)),
    estimate = t_test[[1]]$estimate,
    statistic = t_test[[1]]$statistic,
    p_value = t_test[[1]]$p.value,
    conf_int_low = t_test[[1]]$conf.int[1],
    conf_int_high = t_test[[1]]$conf.int[2],
    df = t_test[[1]]$parameter,
    effect_size = as.numeric(cohensD(Affirming, mu = 0))
  ) %>%
  ungroup()
```

# Checking If Effect of Relationship Type on DVs is Moderated by Hyp/Recall
```{r}
Expression %>%
  filter(!is.na(Connection)) %>%
  group_by(Relationship_Type) %>%
  summarise(Recall = mean(Hyp_Recall == "Recall"),
            Hyp = mean(Hyp_Recall == "Hyp"))
```

```{r}
bin.model <- glm(as.factor(Hyp_Recall) ~ Relationship_Type,
               family = binomial, data = subset(Expression, !is.na(Connection)))

summary(bin.model)
confint(bin.model)

exp(coef(bin.model))
exp(confint(bin.model))
```

## Connection
```{r}
model5 <- glm(Connection ~ Relationship_Type * Hyp_Recall, data = subset(Expression, !is.na(Connection)))
summary(model5)
confint(model5)
```

## Draw Close
```{r}
model6 <- glm(DrawClose ~ Relationship_Type * Hyp_Recall, data = subset(Expression, !is.na(DrawClose)))
summary(model6)
confint(model6)
```

## Affirm
```{r}
model7 <- glm(Affirming ~ Relationship_Type*Hyp_Recall, data = subset(Expression, !is.na(Affirming)))
summary(model7)
confint(model7)
```

# Individual Emotion and Relationship Type

## Experience
```{r}
model8 <- glm(Frequency ~ Relationship_Type*Emotion,
              data = subset(Experience, Hyp_Recall == "Recall"))
summary(model8)
```

```{r}
model8.emm <- emmeans(model8, ~ Relationship_Type*Emotion)
pairs(model8.emm)
confint(pairs(model8.emm))
eff_size(model8.emm, sigma = sigma(model8), edf = df.residual(model8))
```

## Expression
```{r}
model9 <- glm(Frequency ~ Relationship_Type*Emotion,
              data = subset(Expression, Hyp_Recall == "Recall"))
summary(model9)
```

```{r}
model9.emm <- emmeans(model9, ~ Relationship_Type*Emotion)
pairs(model9.emm)
confint(pairs(model9.emm))
eff_size(model9.emm, sigma = sigma(model9), edf = df.residual(model9))
```

# Full Descriptive Statistics
```{r}
# Experience
Experience.desc <- apa.2way.table(
  iv1 = Relationship_Type,
  iv2 = Emotion, 
  dv = Frequency,
  data = subset(Experience, Hyp_Recall == "Recall")
)

# Expression
Expression.desc <- apa.2way.table(
  iv1 = Relationship_Type,
  iv2 = Emotion, 
  dv = Frequency,
  data = subset(Expression, Hyp_Recall == "Recall")
)

# Connection
Connection.desc <- apa.2way.table(
  iv1 = Relationship_Type,
  iv2 = Emotion, 
  dv = Connection,
  data = Expression
)

# Affirming
Affirm.desc <- apa.2way.table(
  iv1 = Relationship_Type,
  iv2 = Emotion, 
  dv = Affirming,
  data = Expression
)

# Draw Close
DrawClose.desc <- apa.2way.table(
  iv1 = Relationship_Type,
  iv2 = Emotion, 
  dv = DrawClose,
  data = Expression
)

# Willingness
Willingness.desc <- apa.2way.table(
  iv1 = Relationship_Type,
  iv2 = Emotion, 
  dv = Willing,
  data = subset(Expression, Hyp_Recall == "Recall")
)

Experience.desc
Expression.desc
Connection.desc
Affirm.desc
DrawClose.desc
Willingness.desc
```
