---
title: "Study 4 Primary Analyses"
author: "Muji Chughtai"
date: "`r Sys.Date()`"
output: pdf_document
---

# Load in Required Packages and Data
```{r}
library(tidyverse)
library(here)
library(svglite)
library(lme4)
library(lmerTest)
library(emmeans)
library(lsr)

study4 <- read.csv(
  here("Data", "Analysis-Ready Data", "Study4_AnalysisData.csv")
)
Experience <- study4 %>%
  filter(Exp_Type == "Experience")
Expression <- study4 %>%
  filter(Exp_Type == "Expression")
```

# Demographics

## Race
```{r}
individuals <- study4 %>%
  distinct(PID, .keep_all = TRUE)

individuals %>%
  mutate(Race = if_else(grepl(",", Race), "10", Race)) %>%
  group_by(Race) %>%
  summarise(
    N = n(),
    Proportion = N / nrow(individuals)
  ) %>%
  arrange(desc(N))
```

## Age
```{r}
individuals %>%
  filter(!is.na(Age_4_TEXT)) %>%
  summarise(Min = min(Age_4_TEXT),
            Q1 = quantile(Age_4_TEXT, 0.25),
            Mean = mean(Age_4_TEXT),
            Median = median(Age_4_TEXT),
            Q3 = quantile(Age_4_TEXT, 0.75),
            Max = max(Age_4_TEXT),
            IQR = IQR(Age_4_TEXT),
            SD = sd(Age_4_TEXT),
            N = n())
```

## Gender
```{r}
individuals %>%
  group_by(Gender) %>%
  summarise(
    N = n(),
    Proportion = N / nrow(individuals)) %>%
  arrange(desc(N))
```

# Experience

## Distributions and Summary Statistics
```{r}
Experience %>%
  filter(Hyp_Recall == "Recall") %>%
  filter(!is.na(Frequency)) %>%
  summarise(Min = min(Frequency),
            Q1 = quantile(Frequency, 0.25),
            Mean = mean(Frequency),
            Median = median(Frequency),
            Q3 = quantile(Frequency, 0.75),
            Max = max(Frequency),
            IQR = IQR(Frequency),
            SD = sd(Frequency),
            N = n())
```

```{r}
Experience %>%
  filter(Hyp_Recall == "Recall") %>%
  ggplot(aes(x = Frequency)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), bins = 5, fill = "#228B22", color = "black", ) +
  labs(title = "Frequency of Experience", x = "Frequency",
       y = "Percentage") + theme_minimal()
```

## Checking Normality of Residuals for the Full Model
```{r}
full.model <- glm(Frequency ~ Relationship_Type*Emotion, data = subset(Experience, Hyp_Recall == "Recall"))

x <- ggplot() +
  stat_qq(aes(sample = residuals(full.model)), distribution = qnorm) +
  stat_qq_line(aes(sample = residuals(full.model)), distribution = qnorm) +
  ggtitle("Q-Q Plot") +
  labs(title = "Residuals for Frequency of Perceived Experience",
       x = "Theoretical Quantiles",
       y = "Sample Quantiles") + theme_minimal()


ggsave(
  here("Figures", "Study 4", "Study4_Residuals_Experience.svg"),
  x,
  width = 8,
  height = 6
)
```

# Expression

## Distributions and Summary Statistics
```{r}
Expression %>%
  filter(Hyp_Recall == "Recall") %>%
  filter(!is.na(Frequency)) %>%
  summarise(Min = min(Frequency),
            Q1 = quantile(Frequency, 0.25),
            Mean = mean(Frequency),
            Median = median(Frequency),
            Q3 = quantile(Frequency, 0.75),
            Max = max(Frequency),
            IQR = IQR(Frequency),
            SD = sd(Frequency),
            N = n())
```

```{r}
Expression %>%
  filter(Hyp_Recall == "Recall") %>%
  ggplot(aes(x = Frequency)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), bins = 5, fill = "#228B22", color = "black", ) +
  labs(title = "Frequency of Expression", x = "Frequency",
       y = "Percentage") + theme_minimal()
```

## Checking Normality of Residuals for the Full Model
```{r}
full.model <- glm(Frequency ~ Relationship_Type*Emotion, data = subset(Expression, Hyp_Recall == "Recall"))

x <- ggplot() +
  stat_qq(aes(sample = residuals(full.model)), distribution = qnorm) +
  stat_qq_line(aes(sample = residuals(full.model)), distribution = qnorm) +
  ggtitle("Q-Q Plot") +
  labs(title = "Residuals for Frequency of Perceived Expression",
       x = "Theoretical Quantiles",
       y = "Sample Quantiles") + theme_minimal()

ggsave(
  here("Figures", "Study 4", "Study4_Residuals_Expression.svg"),
  x,
  width = 8,
  height = 6
)
```

# Connection

## Distributions and Summary Statistics
```{r}
Expression %>%
  filter(!is.na(Connection)) %>%
  summarise(Min = min(Connection),
            Q1 = quantile(Connection, 0.25),
            Mean = mean(Connection),
            Median = median(Connection),
            Q3 = quantile(Connection, 0.75),
            Max = max(Connection),
            IQR = IQR(Connection),
            SD = sd(Connection),
            N = n())
```

```{r}
Expression %>%
  ggplot(aes(x = Connection)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), bins = 5, fill = "#228B22", color = "black", ) +
  labs(title = "Feelings of Connection when Expressing", x = "Frequency",
       y = "Percentage") + theme_minimal()
```

## Checking Normality of Residuals for the Full Model
```{r}
full.model <- glm(Connection ~ Relationship_Type*Emotion, data = Expression)

x <- ggplot() +
  stat_qq(aes(sample = residuals(full.model)), distribution = qnorm) +
  stat_qq_line(aes(sample = residuals(full.model)), distribution = qnorm) +
  ggtitle("Q-Q Plot") +
  labs(title = "Residuals for Feelings of Connection",
       x = "Theoretical Quantiles",
       y = "Sample Quantiles") + theme_minimal()

ggsave(
  here("Figures", "Study 4", "Study4_Residuals_Connection.svg"),
  x,
  width = 8,
  height = 6
)
```

# Affirm or Undermine

## Distributions and Summary Statistics
```{r}
Expression %>%
  filter(!is.na(Affirming)) %>%
  summarise(Min = min(Affirming),
            Q1 = quantile(Affirming, 0.25),
            Mean = mean(Affirming),
            Median = median(Affirming),
            Q3 = quantile(Affirming, 0.75),
            Max = max(Affirming),
            IQR = IQR(Affirming), 
            SD = sd(Affirming),
            N = n())
```

```{r}
Expression %>%
  ggplot(aes(x = Affirming)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), bins = 5, fill = "#228B22", color = "black", ) +
  labs(title = "Does Expressing Affirm or Undermine", x = "Frequency",
       y = "Percentage") + theme_minimal()
```

## Checking Normality of Residuals for the Full Model
```{r}
full.model <- glm(Affirming ~ Relationship_Type*Emotion, data = Expression)

x <- ggplot() +
  stat_qq(aes(sample = residuals(full.model)), distribution = qnorm) +
  stat_qq_line(aes(sample = residuals(full.model)), distribution = qnorm) +
  ggtitle("Q-Q Plot") +
  labs(title = "Residuals for Perception as Relationship Affirming/Undermining", x = "Frequency",
       x = "Theoretical Quantiles",
       y = "Sample Quantiles") + theme_minimal()

ggsave(
  here("Figures", "Study 4", "Study4_Residuals_Affirm.svg"),
  x,
  width = 8,
  height = 6
)
```

# Draw Close or Distance

## Distributions and Summary Statistics
```{r}
Expression %>%
  filter(!is.na(DrawClose)) %>%
  summarise(Min = min(DrawClose),
            Q1 = quantile(DrawClose, 0.25),
            Mean = mean(DrawClose),
            Median = median(DrawClose),
            Q3 = quantile(DrawClose, 0.75),
            Max = max(DrawClose),
            IQR = IQR(DrawClose),
            SD = sd(DrawClose),
            N = n())
```

```{r}
Expression %>%
  ggplot(aes(x = DrawClose)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), bins = 5, fill = "#228B22", color = "black", ) +
  labs(title = "Does Expressing Draw Close or Distance", x = "Frequency",
       y = "Percentage") + theme_minimal()
```

## Checking Normality of Residuals for the Full Model
```{r}
full.model <- glm(DrawClose ~ Relationship_Type*Emotion, data = Expression)

x <- ggplot() +
  stat_qq(aes(sample = residuals(full.model)), distribution = qnorm) +
  stat_qq_line(aes(sample = residuals(full.model)), distribution = qnorm) +
  ggtitle("Q-Q Plot") +
  labs(title = "Residuals for Extent to Which Perception Draws Close or Distances",
       x = "Theoretical Quantiles",
       y = "Sample Quantiles") + theme_minimal()

ggsave(
  here("Figures", "Study 4", "Study4_Residuals_DrawClose.svg"),
  x,
  width = 8,
  height = 6
)
```

# Checking Random Effects of Participant

## Experience
```{r}
model <- lmer(Frequency ~ 1 + (1|PID), data = Experience)
summary(model)

ICC <- 0.2272 / (0.2272 + 1.3486);ICC
```

## Expression
```{r}
model <- lmer(Frequency ~ 1 + (1|PID), data = Expression)
summary(model)

ICC <- 0.2588 / (0.2588 + 1.4181);ICC
```

## Connection
```{r}
model <- lmer(Connection ~ 1 + (1|PID), data = Expression)
summary(model)

ICC <- 0.1182 / (0.1182 + 0.8514);ICC
```

## Affirm or Undermine
```{r}
model <- lmer(Affirming ~ 1 + (1|PID), data = Expression)
summary(model)

ICC <- 0.09651 / (0.09651 + 0.92556);ICC
```

## Draw Close or Distance
```{r}
model <- lmer(DrawClose ~ 1 + (1|PID), data = Expression)
summary(model)

ICC <- 0.1273 / (0.1273 + 0.8820);ICC
```

# Testing Preregistered Primary Hypotheses

## H1 - Perceived Experience will be Higher in Communal Relationships
```{r}
model1 <- glm(Frequency ~ Relationship_Type,
              data = subset(Experience, Hyp_Recall == "Recall"))
summary(model1)
confint(model1)
cohensD(Frequency ~ Relationship_Type, data = subset(Experience, Hyp_Recall == "Recall"))
```

## H2 - Expression will be Higher in Communal Relationships
```{r}
model2 <- glm(Frequency ~ Relationship_Type,
              data = subset(Expression, Hyp_Recall == "Recall"))
summary(model2)
confint(model2)
cohensD(Frequency ~ Relationship_Type, data = subset(Expression, Hyp_Recall == "Recall"))
```

## H3 - Connection will be Higher in Communal Relationships
```{r}
model3 <- glm(Connection ~ Relationship_Type, data = Expression)
summary(model3)
confint(model3)
cohensD(Connection ~ Relationship_Type, data = Expression)
```

```{r}
x <- Expression %>%
  filter(!is.na(Connection)) %>%
  ggplot(aes(x = factor(Relationship_Type, levels = c("Communal", "Transactional")),
             fill = factor(Emotion, levels = c("Love", "Joy", "Sadness", "Hurt")),
             y = Connection)) +
    scale_fill_manual(values = c("Love" = "#E57373", "Joy" = "#FFCA28",  
                               "Sadness" = "#64B5F6", "Hurt" = "#AF7AC5")) +
  stat_summary(fun = "mean", geom = "col", color = "black", position = "dodge") +
  stat_summary(fun.data = "mean_cl_normal", geom = "errorbar",
               position = position_dodge(0.9), width = 0.25) +
  labs(title = "",
       x = "Relationship Type",
       y = "Rating",
       fill = "Emotion") +
    coord_cartesian(ylim = c(-2, 2)) + 
    theme_minimal() + 
    theme(
        legend.position = "bottom", 
        strip.text = element_text(size=14),
        axis.text = element_text(size=14),
        axis.title.y = element_text(size=14, vjust=0.35),
        axis.title.x = element_text(size=16),
        legend.title = element_text(size=16),
        legend.text = element_text(size=14),
        text = element_text(family = "Helvetica")
    )

ggsave(
  here("Figures", "Study 4", "Study4_Connection.svg"),
  x,
  width = 8,
  height = 6
)
```

## H4 - Expression will be More Relationship-Affirming in Communal Relationships
```{r}
model4 <- glm(Affirming ~ Relationship_Type, data = Expression)
summary(model4)
confint(model4)
cohensD(Affirming ~ Relationship_Type, data = Expression)
```

```{r}
x <- Expression %>%
  filter(!is.na(Affirming)) %>%
  ggplot(aes(x = factor(Relationship_Type, levels = c("Communal", "Transactional")),
             fill = factor(Emotion, levels = c("Love", "Joy", "Sadness", "Hurt")),
             y = Affirming)) +
    scale_fill_manual(values = c("Love" = "#E57373", "Joy" = "#FFCA28",  
                               "Sadness" = "#64B5F6", "Hurt" = "#AF7AC5")) +
  stat_summary(fun = "mean", geom = "col", color = "black", position = "dodge") +
  stat_summary(fun.data = "mean_cl_normal", geom = "errorbar",
               position = position_dodge(0.9), width = 0.25) +
  labs(title = "",
       x = "Relationship Type",
       y = "Rating",
       fill = "Emotion") +
    coord_cartesian(ylim = c(-2, 2)) + 
    theme_minimal() + 
    theme(
        legend.position = "bottom", 
        strip.text = element_text(size=14),
        axis.text = element_text(size=14),
        axis.title.y = element_text(size=14, vjust=0.35),
        axis.title.x = element_text(size=16),
        legend.title = element_text(size=16),
        legend.text = element_text(size=14),
        text = element_text(family = "Helvetica")
    )

ggsave(
  here("Figures", "Study 4", "Study4_Affirm.svg"),
  x,
  width = 8,
  height = 6
)
```

## H5 - Expression will Draw Closer in Communal Relationships
```{r}
model5 <- glm(DrawClose ~ Relationship_Type, data = Expression)
summary(model5)
confint(model5)
cohensD(DrawClose ~ Relationship_Type, data = Expression)
```

```{r}
x <- Expression %>%
  filter(!is.na(DrawClose)) %>%
  ggplot(aes(x = factor(Relationship_Type, levels = c("Communal", "Transactional")),
             fill = factor(Emotion, levels = c("Love", "Joy", "Sadness", "Hurt")),
             y = DrawClose)) +
    scale_fill_manual(values = c("Love" = "#E57373", "Joy" = "#FFCA28",  
                               "Sadness" = "#64B5F6", "Hurt" = "#AF7AC5")) +
  stat_summary(fun = "mean", geom = "col", color = "black", position = "dodge") +
  stat_summary(fun.data = "mean_cl_normal", geom = "errorbar",
               position = position_dodge(0.9), width = 0.25) +
  labs(title = "",
       x = "Relationship Type",
       y = "Rating",
       fill = "Emotion") +
    coord_cartesian(ylim = c(-2, 2)) + 
    theme_minimal() + 
    theme(
        legend.position = "bottom", 
        strip.text = element_text(size=14),
        axis.text = element_text(size=14),
        axis.title.y = element_text(size=14, vjust=0.35),
        axis.title.x = element_text(size=16),
        legend.title = element_text(size=16),
        legend.text = element_text(size=14),
        text = element_text(family = "Helvetica")
    )

ggsave(
  here("Figures", "Study 4", "Study4_DrawClose.svg"),
  x,
  width = 8,
  height = 6
)
```
